The impact of gas bulk rotation on the Lyman $\alpha$ line

### 2014-04-24 paper/ms.tex
More text + figures etc..

\shortauthors{Garavito-Camargo, Forero-Romero \& Dijstra}

@@

Figure \ref{fig:differentvelocities} shows the clear
impact of rotation on the morphology of the emergent \ly line,
This profiles were obtained integrating the flux of photons 
 over the angle $\theta = \pi/2$, this means we made histograms of the 
 numbers of photons escaping the galaxy with a given frequency
The panel focus on the results for all of our symmetric models
 $\tau_{H}=(10^{5}, 10^{6}, 10^{7}$), showing that the
influence of rotation is present both when the photons are either
homogeneously or centrally initialized over the gas volume.

In the next subsections we characterize the line morphology by the
full width at half maximum (FWHM) and the location of the peak
maxima. In order to interpret the morphological changes in the line we
also report the median number of scatter for each \ly photon in the
simulation. For the models where dust is included we measure the 
escape fraction as a function of rotational velocity. Finally, we make
an estimate of the impact of anisotropic emission.

@@

\begin{figure*}
\begin{center}
  \includegraphics[width=0.8\textwidth]{widths.eps}
\end{center}
  \caption{FWHM for the non-dusty models as a function of
    rotational velocity $V_{\rm max}$. The left panel shows the
    results in velocity units while the right panel normalizes
    the data by the FWHM in the static case. 
    Continuous (dashed) lines  correspond to central (homogeneous)
    source distributions. The straight lines represent the fit to
    the data using the expression in Eq. (\ref{eq:fwhm}).
    \label{fig:widthvsvelocity}} 
\end{figure*}

@@

We use the full width at half maximum (FWHM) to quantify the line
broadening. For this we measure the width by interpolating dots in 
our spectra this would produce a continuous spectra which makes easier
to find the half maximum in our histogram numerically, just finding the 
values of the width at the half maximum.

>>>>

\shortauthors{Garavito-Camargo, Forero-Romero \& Dijkstra}

@@

Figure \ref{fig:differentvelocities} shows the clear
impact of rotation on the morphology of the emergent \ly line.
This profiles were obtained integrating the flux of photons 
 over the angle $\theta = \pi/2$, this means we have made histograms of the 
 numbers of photons escaping the galaxy with a given frequency
The panel focus on the results for all of our symmetric models
 $\tau_{H}=(10^{5}, 10^{6}, 10^{7}$), showing that the
influence of rotation is present both when the photons are either
homogeneously or centrally initialized over the gas volume.

In the next subsections we characterize the line morphology by the
full width at half maximum (FWHM) and the location of the peak
maxima. In order to interpret the morphological changes in the line we
also report the median number of scatter for each \ly photon in the
simulation. For the models where dust is included we measure the 
escape fraction as a function of rotational velocity.

\subsection{Rotation and the spherical symmetry}

As a first approach we study the symmetry of the out-coming spectra
taking into account the line of view ($\theta$) of an observer. Figures 
\ref{fig:CentralSpec} and \ref{fig:HOMSpec} shows our findings, for 
both distributions the morphology of the line change as the line 
of sight of and observer changes. This is mainly due to the fact
that photons propagating at $\theta = pi/2.0$ feel an stronger 
angular momentum showing ... while photons in other direction feel
a less contribution.

We also consider possible variations in the flux with respect to $\theta$.
 We define the flux by:
\begin{equation}
F(\mu) = \frac{2\Delta N}{N\Delta \mu}, 
\end{equation}

Where $\mu=\cos\Theta$, $N$ is the total number of outgoing photons,
$\Delta N$ is the number of photons in an angular bin $\Delta
\Theta$. This definition satisfies the condition
$\int_{-1}^{1}F(\mu)d\mu/2=1$.  With this definitions, the 
emission is characterized by a flat $F(\mu)$ distribution as 
is shown in \ref{fig:muhisto}, this means that the amount of flux
is the same for all of the angles.

\begin{figure}
\begin{center}
  \includegraphics[width=0.4\textwidth]{muhisto.eps}
\end{center}
\caption{Position of the peak maxima as a function of rotational
  velocity $V_{\rm max}$. Continuous (dashed) lines correspond to
  central (homogeneous) source distributions. A value of $x_{\rm
    max}=0$ indicates that line becomes single
  peaked. \label{fig:muhisto}}  
\end{figure}

Taking into account these results we perform the subsequent analysis
for a fixed observer at $\theta = \pi/2.0$, the effect in the morphology
of the \lya	line for different velocities is clearly shown in Figure
 \ref{fig:differentvelocities}

@@

\begin{figure*}
\begin{center}
  \includegraphics[width=0.8\textwidth]{widths.eps}
\end{center}
  \caption{FWHM for the non-dusty models as a function of
    rotational velocity $V_{\rm max}$. The left panel shows the
    results in velocity units while the right panel normalizes
    the data by the FWHM in the static case. 
    Continuous (dashed) lines  correspond to central (homogeneous)
    source distributions. The straight lines represent the fit to
    the data using the expression in Eq. (\ref{eq:fwhm}).
    \label{fig:widthvsmu}} 
\end{figure*}

@@

We use the full width at half maximum (FWHM) to quantify the line
broadening. For this we measure the width by interpolating dots in 
our spectra this would produce a continuous spectra which makes easier
to find the half maximum in our histogram numerically, just finding the 
values of the width at the half maximum. In Figure \ref{fig:widthvsmu}
the effect of the viewing angle is shown, the main effects here are that 
as $\mu$ increase the FWHM decrease this is also explained by the same argument
of section XX. The second effect is that clearly as $\rm{V_{max}}$ increase 
the FWHM also increase.

\begin{figure*}
\begin{center}
  \includegraphics[width=0.8\textwidth]{f2.eps}
\end{center}
\caption{Position of the peak maxima as a function of rotational
  velocity $V_{\rm max}$. Continuous (dashed) lines correspond to
  central (homogeneous) source distributions. A value of $x_{\rm
    max}=0$ indicates that line becomes single
  peaked. \label{fig:widthsvsvelocity}}  
\end{figure*}
